---
title: "Extraction et calcul des anamolies climatiques"
author: "Romain Lorrilliere, Yves Bas (CesCO, MNHN)"
date: "07/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("f_coord_date_weather.r")
# rmarkdown::render("get_weather.rmd",output_file="get_weather")
```

```{r , eval=TRUE, echo=TRUE}
source("f_coord_date_weather.r")
library(data.table)
library(dplyr)
```


## Open file


## Weather data extraction from nc files and saving in rData format

default value of parameters: 
	* firstYear = 1950
	* lastYear = last available year
	* repout = data

```{r, eval=FALSE, echo=TRUE}
nc2rdata()

```




## Assessing reference value of daily weather (temprature mean and
precipitation)

default value of parameters: 

	* firstYear = 1950
	* lastYear = last available year
	* repout = data


##' @param first_year
##' @param last_year
##' @param nc_one_file
##' @param nc_local
##' @param nc_extract
##' @param nc_data
##' @param nc_rep
##' @param file_nc_out
##' @param var
##' @param dsample_colnames
##' @param output
##' @param save
##' @param fileouput


```{r,eval=FALSE,echo=TRUE}
assess_weather_ref()

```














```{r,eval=FALSE}
d <- gen_import_fread()
dsample <- unique(d[,c("date_format","longitude","latitude")])
dsite <- unique(d[,c("longitude","latitude")])
dsite$site_id <- 1:nrow(dsite)

dsample <- data.table(inner_join(dsample,dsite))

```


```{r, eval=FALSE}
get_sample_weather()


```


